---
title: "Marketing Analytics"
listing: 
  contents: listings
  type: grid
  categories: true
  sort: 
    - "index desc"
---

Below are selected projects that highlight my experience applying marketing analytics to the day-to-day and strategic operations of a specialty coffee shop. These examples demonstrate how I use data-driven insights to improve customer engagement, optimize promotional efforts, and grow the business.

From tracking in-store promotions to analyzing social media performance and customer behavior, each project reflects my ability to turn real-world marketing data into actionable strategies that enhance both brand presence and profitability.

## What You’ll Find

- **Campaign Performance Analysis:** Measuring the impact of seasonal promotions, local ads, and social media campaigns on foot traffic and sales.
- **Data Visualization:** Building intuitive dashboards to monitor daily performance metrics, customer trends, and marketing ROI.
- **Channel & Offer Attribution:** Identifying which marketing channels (e.g., Instagram, Google Maps, email) and offers are driving the most customer engagement and repeat visits.
- **Customer & Market Insights:** Using POS data, survey feedback, and web analytics to better understand buying habits, peak times, and menu preferences.

---

```{r}


library(ggplot2)
# Your exact data
data <- structure(list(
  Channel = c("Instagram", "Google Maps", "Email Newsletter", "In-store Posters"), 
  Revenue = c(4200, 3100, 1800, 950)), 
  class = "data.frame", row.names = c(NA, -4L))

# Plot with explicit data reference
ggplot(data, aes(x = reorder(.data$Channel, .data$Revenue), 
             y = .data$Revenue, 
             fill = .data$Channel)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Campaign Performance by Channel",
       x = "Marketing Channel",
       y = "Revenue Generated ($)") +
  theme_minimal() +
  geom_text(aes(label = Revenue), hjust = -0.1, size = 3) +  # Add value labels
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))    # Make space for labels
```

```{r}
library(ggplot2)

weeks <- c("Week 1", "Week 2", "Week 3", "Week 4")
traffic <- c(180, 230, 210, 275)

data <- data.frame(Week = weeks, Customers = traffic)

ggplot(data, aes(x = Week, y = Customers)) +
  geom_line(color = "forestgreen", size = 1.2) +
  geom_point(color = "darkgreen", size = 3) +
  labs(title = "Weekly Foot Traffic After Instagram Promotions",
       x = "Week",
       y = "Customer Count") +
  theme_minimal()
```
  
