---
name: Miguel
surname: Lau
position: "Business Owner"
phone: +1 (626) 534-1923
www: 
email: "mlauzhou@gmail.com"
github: miguellau94
linkedin: Miguel Lau
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Results-driven business owner and operations manager with over a decade of experience leading teams, optimizing business performance, and delivering exceptional customer service across the food service, retail, automotive, and manufacturing sectors. Proven success as the owner and manager of a specialty coffee shop, overseeing daily operations, financial planning, staff development, inventory control, and marketing initiatives. Skilled in sales and account management with a strong track record of exceeding targets and building lasting client relationships. Adept at managing multimillion-dollar inventories, streamlining workflows, and improving quality standards in high-volume environments. Known for strategic thinking, hands-on leadership, and a passion for building strong teams and efficient, customer-focused businesses.


# Technical Skills

Business & Financial Operations: Financial Planning · Accounting · Account Management · Inventory Control · Cost Analysis


Leadership & Management: Team Leadership · Team Management · Staff Training & Development · Operations Management · Quality Assurance · Production Oversight


Sales & Customer Experience: Sales Management · Customer Service · Relationship Building · Deal Negotiation


Marketing & Branding: Marketing Strategy · Social Media Marketing · Brand Development · Promotional Campaigns

# Education

```{r}
tribble(
  ~Degree, ~Year, ~College, ~Institution,
  "Bachelor of Science in Business Administration & Marketing Management", "2021 – 2025", "College of Business Administration", "California Polytechnic State University, Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~Years, ~Company, ~Title, ~Duties,
  
  "September 2022 – Present", "Margin Cafe Coffee Roasters", "Manager / Owner",
  "As the owner of Margin Café, I am responsible for overseeing all aspects of the café’s operations, from daily management to long-term business strategy. I handle inventory management, supplier relationships, and financial planning to ensure profitability while maintaining high standards of quality and customer service. I lead a team of staff, providing training, setting performance goals, and fostering a positive work environment. I develop and update the menu, ensuring it aligns with customer preferences and market trends. Additionally, I handle marketing and promotions to attract new customers, build brand loyalty, and increase sales. I focus on creating a welcoming atmosphere and ensuring that every guest has an exceptional dining experience.",
  
  "March 2021 – May 2022", "T&J Garden Supply", "Assistant Manager",
  "In my role as Assistant Manager at a T&J Garden Supply store, I was responsible for overseeing the day-to-day operations of the store, with a focus on managing an inventory valued at over $500k. I ensured stock levels were maintained, conducted regular inventory audits, and handled ordering and restocking to meet demand. I also assisted in managing and training staff to provide excellent customer service and ensured the store was organized and visually appealing. Additionally, I addressed customer inquiries, resolved issues, and supported the Store Manager in achieving operational goals."
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```